\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.3 in,top=0.3in,right=0.3 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sahil Vishwakarma} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{3rd Year UG, Computer Science Engineering} 
\address{\href{mailto:sahilvishwa2108@gmail.com}{sahilvishwa2108@gmail.com} | +91 7440207015 | \href{https://linkedin.com/in/sahilvishwa2108}{linkedin.com/in/sahilvishwa2108} | \href{https://github.com/Sahilvishwa2108}{github.com/Sahilvishwa2108} | LeetCode | Bhopal}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\vspace{-0.5em}
{\bf Lakshmi Narain College of Technology, Bhopal} \hfill {Expected July 2026}\\
\vspace{-0.3em}B. Tech in Computer Science Engineering \hfill {8.12 CGPA}

\vspace{-0.3em}{\bf Jawahar Navodaya Vidyalaya, Sagar} \hfill {April 2021}\\
\vspace{-0.3em}XII (CBSE) with Computer Science \hfill {91.6\%}

\vspace{-0.3em}{\bf Jawahar Navodaya Vidyalaya, Sagar} \hfill {April 2019}\\
\vspace{-0.3em}X (CBSE) \hfill {92.4\%}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\vspace{-0.5em}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Java, JavaScript, TypeScript, SQL, Git, HTML, CSS
\\
Developer Tools & Node.js, GitHub Actions, MongoDB, Prisma, PostgreSQL, Postman, Redis, Linux, Docker, Packet Tracer
\\
Libraries/Frameworks & Next.js, React.js, Tailwind CSS, Framer motion, Three.js
\\
Core Subjects & OOPs, DBMS, Operating Systems, Computer Networks
\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}
\vspace{-0.5em}
\textbf{Freelance Full Stack Developer} \hfill March 2025 | April 2025\\
Mukul Verma \& Co. \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -4pt {} 
     \item Built an office management SaaS with task delegation, client/user management, real-time chat, and history tracking.
     \item Designed multi-tier RBAC and role-based dashboards with tailored analytics, feeds, and task overviews.
     \item Implemented core workflows for task assignment, priority, billing approval, status tracking, and notifications.
     \item Ensured reliability with validation, error handling, audit logging, and background jobs for expiry, cleanup, and maintenance.
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.5em}
\item \textbf{Office Pilot | Workspace Management SaaS | Link |}
\begin{itemize}
    \itemsep -4pt {}
    \item Built full-stack SaaS for task/client management using Next.js, TypeScript, Tailwind, Prisma, PostgreSQL, Redis, Cloudinary, and more.
    \item Designed typed-enum M2M schema; improved performance with debounced search, Lazy loading, SSR, and cursor-based pagination.
    \item Implemented real-time chatroom and notification system via Redis pub/sub; automated workflows using queue-based cron jobs.
    \item Secured app with RBAC, memoization, and cache invalidation; added circular logging and multi-level caching for reliability.
    \item Delivered responsive UI with theme toggle, local storage, and full-screen UX enhancements.
\end{itemize}
\vspace{-0.5em}
\item \textbf{True Feedback | AI Powered PWA | Link |}
\begin{itemize}
    \itemsep -4pt {}
    \item Built anonymous feedback collection platform using Next.js, React, TypeScript with OAuth, OTP validation, JWT, NextAuth and bcrypt.
    \item Integrated OpenAI API and Vercel AI SDK for AI-generated suggestions and category-wise feedback filtering.
    \item Designed a fully animated, responsive UI using Tailwind CSS, Framer Motion, and Lucide-react for an engaging experience.
    \item Handled secure feedback storage and dashboard updates via MongoDB/Mongoose; validated forms with Zod \& React Hook Form.
\end{itemize}
\vspace{-0.5em}
\item \textbf{Oil Spill Detection System | Group Project | Link |}
\begin{itemize}
    \itemsep -4pt {}
    \item Developed ML inference pipeline (U-Net, DeepLabV3+) using Python \& FastAPI, integrated with Hugging Face for 95\%+ accuracy.
    \item Designed a dashboard in Next.js 15 (SSR) to visualize segmentation of oil spills and confidence scores.
    \item Containerized the backend using Docker and deployed it on Render, with optimized image pipelines, and secure CORS configuration.
    \item Set up CI/CD workflows via GitHub Actions for linting, Docker builds, and auto-deploy to Vercel and Render.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications}
\vspace{-0.5em}
\textbf{NPTEL:} Programming in Java | Database Management System | Computer Networks | Python Essentials 1 | Python Essentials 2 \\
\textbf{AWS:} Cloud Foundation Certifications \\
\textbf{Cisco:} CCNA Certifications | Introduction to Cyber Security
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}
\vspace{-0.5em}
\begin{itemize}
    \itemsep -4pt {}
    \item Contributed to innovative solutions during SIH 2024 and other Hackathons, emphasizing teamwork and coding expertise.
    \item Secured AIR 1864 in AINCAT (All India Naukri Campus Aptitude Test) - 2025
\end{itemize}
\end{rSection}


\end{document}
